### 2020-07-26 draft.Rmd
run JT test

```{r r-setup}
library(tidyverse)
library(haven) # reading Stata data
library(MASS) # M-estimation
library(Rfit) # rank-based regression
library(patchwork)
library(broom)
library(sandwich)
library(lmtest)

@@

@@

>>>>

```{r r-setup}
library(tidyverse)
library(haven) # reading Stata data
library(MASS) # M-estimation
library(Rfit) # rank-based regression
library(patchwork)
library(broom)
library(sandwich)
library(lmtest)
library(NSM3)

@@

```{r k-sample JT test}

seed_balchange = seed_accounts$balchange
marketing_balchange = (treated %>% filter(marketing==1))$balchange
control_balchange = (treated %>% filter(control==1, marketing==0))$balchange
x = list(control_balchange, marketing_balchange, seed_balchange)
pJCK(x, method="Monte Carlo")

@@

A p-value of 0.0001 means that we reject the null hypothesis in favor of the alternate.
